The K2 Bright Star Survey

### 2019-05-07 paper/ms.tex
bit about softmax

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

>>>>

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution. In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
